|

### 2020-10-08 manuscript.Rmd
minor updates in plotting the dance of the BFs

# plotting the results
results %>%
  pivot_longer(cols = BF10:BF10_double, names_to = "type") %>%
  mutate(
    type = factor(
      type,
      levels = c("BF10_null", "BF10", "BF10_double"),
      labels = c("Cohen's d = 0", "Cohen's d = 0.36", "Cohen's d = 0.72")
      )
    ) %>%
  ggplot(aes(x = log(value), fill = type) ) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_vline(xintercept = log(0.278), linetype = 2, colour = "orangered") +
  geom_histogram(colour = "white", show.legend = FALSE, bins = 50) +
  theme_bw(base_size = 12) +
  facet_wrap(~ type, scales = "free_x") +
  labs(x = "Natural logarithm of the BF10", y = "Number of simulations") +
  scale_colour_brewer(palette = "Dark2", direction = 1) +
  scale_fill_brewer(palette = "Dark2", direction = 1)

# computing the proportion of simulated BFs above 1
prop_d0 <- mean(results$BF10_null > 1)
prop_d0.36 <- mean(results$BF10 > 1)
prop_d0.72 <- mean(results$BF10_double > 1)
```

>>>>

# computing the proportion of simulated BFs above 1
prop_d0 <- mean(results$BF10_null > 1)
prop_d0.36 <- mean(results$BF10 > 1)
prop_d0.72 <- mean(results$BF10_double > 1)

# plotting the results
results %>%
  pivot_longer(cols = BF10:BF10_double, names_to = "type") %>%
  mutate(
    type = factor(
      type,
      levels = c("BF10_null", "BF10", "BF10_double"),
      labels = c("Cohen's d = 0", "Cohen's d = 0.36", "Cohen's d = 0.72")
      )
    ) %>%
  ggplot(aes(x = log(value), colour = type, fill = type) ) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_vline(xintercept = log(0.278), linetype = 2, colour = "orangered") +
  geom_histogram(colour = "white", show.legend = FALSE, bins = 40) +
  theme_bw(base_size = 12) +
  facet_wrap(~ type, scales = "free_x") +
  labs(x = "Natural logarithm of the BF10", y = "Number of simulations") +
  scale_colour_brewer(palette = "Dark2", direction = 1) +
  scale_fill_brewer(palette = "Dark2", direction = 1) +
  scale_y_continuous(expand =  expansion(mult = c(0, 0.1) ) )
```
